---
title: "Brief analysis of Recla data"
output: html_document
---

```{r options, echo=FALSE}
knitr::opts_chunk$set(fig.width=11, fig.height=6,
                      message=FALSE, warning=FALSE)
```


This is a quick analysis of the data from Recla et al. (2014)
and Logan et al (2013), available at
<https://github.com/rqtl/qtl2data/tree/master/DO_Recla>

We first load the data directly from the web.

```{r load_data}
library(qtl2)
file <- paste0("https://raw.githubusercontent.com/rqtl/",
               "qtl2data/master/DO_Recla/recla.zip")
recla <- read_cross2(file)
```

We calculate genotype probabilities. I use `n_cores <- 0`
throughout (which detects the number of available CPU cores and uses
all of them). If you have limited wRAM on your machine, you may need
to change this to `n_cores <- 1`.

```{r calc_genoprob}
n_cores <- 0
probs <- calc_genoprob(recla, cores=n_cores)
```

We now convert the genotype probabilities to haplotype dosages.

```{r genoprob_to_alleleprob}
aprobs <- genoprob_to_alleleprob(probs, cores=n_cores)
```

We now calculate kinship matrices, by the "leave one chromosome out
(loco)" method.

```{r calc_kinship}
kinship <- calc_kinship(aprobs, "loco", cores=n_cores)
```

A genome scan of all phenotypes.

```{r scan1}
out <- scan1(aprobs, recla$pheno, kinship, cores=n_cores)
```

Plot of the results, all in gray except for the trait with the largest
LOD score, in blue.

```{r plot_scan1}
plot(out, recla$gmap, lodcolumn=1, col="gray60",
     ylim=c(0, maxlod(out)*1.05))
for(i in 2:ncol(out))
    plot(out, recla$gmap, lodcolumn=i, col="gray60", add=TRUE)
plot(out, recla$gmap, lodcolumn=5, col="slateblue", add=TRUE)
```

Here are the peaks above 6.5.

```{r lod_peaks}
find_peaks(out, recla$gmap, threshold=6.5)
```
